A systematic search for transiting planets using \KT

### 2015-02-07 ms.tex
fixing \sim
switching to bibtex

@@

Previous studies have developed methods to work with \KT\ data.
\citet{vanderburg-a} extract aperture photometry from the pixel data
and decorrelate with image centroid position, producing light curves for each
star that are ``corrected'' for the spacecraft motion.
These data have produced the first confirmed planet found with
\KT\ \citep{vanderburg-b}.
\citet{crossfield} iteratively construct a robust Gaussian Process
model for the photometry as a function of the measured centroids and de-trend
using the mean prediction from that model.

@@

The methods developed within this paper are highly relevant to the upcoming
\tess\ mission (Cite-Ricker 14).
\tess\ will feature pointing precision of \sim 3 arcseconds (cite),
similar to the level of pointing drift with \KT.
Moreover, the typical star will be only observed for one month at a time, and
the typical transit detection will be at a similar signal-to-noise ratio as
with \KT.

@@

The starting point for analysis is the raw pixel data.
We download the full set of XXX target pixel files for \KT's Campaign 1 from
MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
Then, we extract photometry using fixed circular apertures of varying sizes
centered on the predicted location of the target star based on the world
coordinate system.
For each time series, we used circular apertures ranging in radius from 0.5 to
5 pixels (in steps of 0.5 pixels) and---following \citet{vanderberg-a}---chose
the aperture size that resulted in the smallest CDPP \dfmtodo{CITE CDPP-Jessie
Christiansen, Jon Jenkins, et al 2012} with a 6 hour window.\footnote{Note
that although we chose a specific aperture, photometry for every aperture size
is available online at \dfmtodo{some URL}.}

Most methods for analyzing \KT\ data---and \kepler\ data, for that
matter---involve some sort of pre-processing or ``de-trending'' step.
For example, \citet{vanderberg-a} measure the centroid motion for each star
and regress out any signal in their aperture photometry that can be fit by
this motion.
Similarly, \citet{crossfield} iteratively construct a robust Gaussian Process
model for the photometry as a function of the measured centroids and de-trend
using the mean prediction from that model.
In our analysis, we don't do any further preprocessing of the light curves
because, as we describe in the next section, we simultaneously fit for the
trends and the transit signals that we are searching for.

One key realization that is also exploited by the official \kepler\ pipeline
is that the systematic trends caused by pointing shifts and other instrumental
effects are shared---with different signs and weights---by all the stars on
the detector.
To make use of this, the \project{PDC} component of the \kepler\ pipeline
removes any trends from the light curves that can be fit using a linear
combination of a small number of ``eigen-light curves'' (ELCs) found by
running Principal Component Analysis (PCA) on a set of light curves
\citep{map-pdc1, map-pdc2}.
Similarly, we ran PCA on the full set of Campaign 1 light curves to determine
a basis of representative ELCs.
We chose to use the top 150 components---many more than are normally
used---for our model described in the following section.
\Fig{pca} shows the top few ELCs.

@@

Physically, the motivation for our model---and the PDC model---is that every
star on the detector should be affected by same set of systematic effects.
These are caused by things like pointing jitter, temperature variations, and
other sources of PSF modulation and each one will be imprinted in the light
curves of many stars with varying amplitudes and signs.
Therefore, while it is hard to write down a physical generative model for the
systematics, building a data-driven model might be possible.
This intuition is also exploited by other methods that model the systematics
using only empirical centroids \citep{vanderberg-a, crossfield} but out more
flexible model should capture the systematic effects more robustly but there
is a risk of over-fitting.
\Fig{corr} shows the application of this model to a light curve with no known
transit signals.

@@

A major problem with any transit search is the potential confusion between
transiting planets and eclipsing binaries.
Ground-based surveys before \kepler\ often had a false-positive rate
of 30-40\%. (because of shit?)
In the primary \kepler\ mission, this number was significantly lower:
the false positive rate was only 5-10\% \citep{morton11}.
Such improvement was enabled by the relatively small pixels, stable
pointing, and high precision of \kepler.
In \kepler\ data, false positives can be reliably separated from
planet candidates by looking for differences in the position of the
centroid of light during transit events with respect to the
out-of-transit data (e.g. citation), variations in the depth of
alternating transits (e.g. citation), and evidence for ellipsoidal
variations between transits (e.g. citation).

@@

\newcommand{\arxiv}[1]{\href{http://arxiv.org/abs/#1}{arXiv:#1}}
\begin{thebibliography}{}\raggedright

\bibitem[Crossfield \etal(2015)]{crossfield}
Crossfield, I.~J.~M., Petigura, E., Schlieder, J., \etal\ 2015,
\arxiv{1501.03798}

\bibitem[Lang \etal(2010)]{astrometry}
Lang, D., Hogg, D.~W., Mierle, K., Blanton, M., \& Roweis, S.\ 2010, \aj, 139,
1782

\bibitem[Pedregosa \etal(2011)]{sklearn}
Pedregosa, F., Varoquaux, G., Gramfort, A., \etal\ 2011, JMLR, 12, 2825

\bibitem[Smith \etal(2012)]{map-pdc2}
Smith,~J.~C., Stumpe,~M.~C., Van Cleve,~J.~E., \etal\ 2012,
\pasp, 124, 1000

\bibitem[Stumpe \etal(2012)]{map-pdc1}
Stumpe,~M.~C., Smith,~J.~C., Van Cleve,~J.~E., \etal\ 2012,
\pasp, 124, 985

\bibitem[Vanderburg \& Johnson(2014a)]{vanderberg-a}
Vanderburg, A., \& Johnson, J.~A.\ 2014, \pasp, 126, 948

\bibitem[Vanderburg \etal(2014b)]{vanderburg-b}
Vanderburg, A., Montet, B.~T., Johnson, J.~A., \etal\ 2014, \arxiv{1412.5674}

\end{thebibliography}

>>>>

\usepackage{natbib}
\bibliographystyle{apj}

@@

Previous studies have developed methods to work with \KT\ data.
\citet{Vanderburg:2014} extract aperture photometry from the pixel data
and decorrelate with image centroid position, producing light curves for each
star that are ``corrected'' for the spacecraft motion.
These data have produced the first confirmed planet found with
\KT\ \citep{Vanderburg:2015}.
\citet{Crossfield:2015} iteratively construct a robust Gaussian Process
model for the photometry as a function of the measured centroids and de-trend
using the mean prediction from that model.

@@

The methods developed within this paper are highly relevant to the upcoming
\tess\ mission (Cite-Ricker 14).
\tess\ will feature pointing precision of $\sim 3$ arcseconds (cite),
similar to the level of pointing drift with \KT.
Moreover, the typical star will be only observed for one month at a time, and
the typical transit detection will be at a similar signal-to-noise ratio as
with \KT.

@@

The starting point for analysis is the raw pixel data.
We download the full set of XXX target pixel files for \KT's Campaign 1 from
MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
Then, we extract photometry using fixed circular apertures of varying sizes
centered on the predicted location of the target star based on the world
coordinate system.
For each time series, we used circular apertures ranging in radius from 0.5 to
5 pixels (in steps of 0.5 pixels) and---following
\citet{Vanderburg:2014}---chose the aperture size that resulted in the
smallest CDPP \citep{cdpp}
with a 6 hour window.\footnote{Note that although we chose a specific
aperture, photometry for every aperture size is available online at
\dfmtodo{some URL}.}

Most methods for analyzing \KT\ data---and \kepler\ data, for that
matter---involve some sort of pre-processing or ``de-trending'' step.
For example, \citet{Vanderburg:2014} measure the centroid motion for each star
and regress out any signal in their aperture photometry that can be fit by
this motion.
Similarly, \citet{Crossfield:2015} iteratively construct a robust Gaussian
Process model for the photometry as a function of the measured centroids and
de-trend using the mean prediction from that model.
In our analysis, we don't do any further preprocessing of the light curves
because, as we describe in the next section, we simultaneously fit for the
trends and the transit signals that we are searching for.

One key realization that is also exploited by the official \kepler\ pipeline
is that the systematic trends caused by pointing shifts and other instrumental
effects are shared---with different signs and weights---by all the stars on
the detector.
To make use of this, the \project{PDC} component of the \kepler\ pipeline
removes any trends from the light curves that can be fit using a linear
combination of a small number of ``eigen-light curves'' (ELCs) found by
running Principal Component Analysis (PCA) on a set of light curves
\citep{pdc1, pdc2}.
Similarly, we ran PCA on the full set of Campaign 1 light curves to determine
a basis of representative ELCs.
We chose to use the top 150 components---many more than are normally
used---for our model described in the following section.
\Fig{pca} shows the top few ELCs.

@@

Physically, the motivation for our model---and the PDC model---is that every
star on the detector should be affected by same set of systematic effects.
These are caused by things like pointing jitter, temperature variations, and
other sources of PSF modulation and each one will be imprinted in the light
curves of many stars with varying amplitudes and signs.
Therefore, while it is hard to write down a physical generative model for the
systematics, building a data-driven model might be possible.
This intuition is also exploited by other methods that model the systematics
using only empirical centroids \citep{Vanderburg:2014, Crossfield:2015} but
out more flexible model should capture the systematic effects more robustly
but there is a risk of over-fitting.
\Fig{corr} shows the application of this model to a light curve with no known
transit signals.

@@

A major problem with any transit search is the potential confusion between
transiting planets and eclipsing binaries.
Ground-based surveys before \kepler\ often had a false-positive rate
of 30-40\%. (because of shit?)
In the primary \kepler\ mission, this number was significantly lower:
the false positive rate was only 5-10\% \citep{Morton:2011}.
Such improvement was enabled by the relatively small pixels, stable
pointing, and high precision of \kepler.
In \kepler\ data, false positives can be reliably separated from
planet candidates by looking for differences in the position of the
centroid of light during transit events with respect to the
out-of-transit data (e.g. citation), variations in the depth of
alternating transits (e.g. citation), and evidence for ellipsoidal
variations between transits (e.g. citation).

@@

\bibliography{k2}
